### Q0: Sampling and Distribution

You are studying the population of a specific type of marine algae in different locations. Assume the algal density is normally distributed. You take samples from two locations (Location A and Location B) to compare the algae populations. Generate synthetic data to represent the algal density (individuals per square meter) at these two locations. Assume a mean density of 200 and 220 individuals/m^2 with a common standard deviation of 20 individuals/m^2 for both locations, with 50 samples from each location.


```{r}
#Set the seed for reproducibility
set.seed(123)

#Parameters
mean_a <- 200
mean_b <- 220
stdev <- 20
sample_size <- 50

#Generate data for Location A
location_a <- rnorm(sample_size, mean_a, stdev)
head(location_a)

#Generate data for Location B
location_b <- rnorm(sample_size, mean_b, stdev)
head(location_b)

#Combine data into a data frame
algae_data <- data.frame(
  Location = factor(c(rep("Location A", length(location_a)), rep("Location B", length(location_b)))),
  Density = c(location_a, location_b)
)

#View first few rows of the data
head(algae_data)
```

### Q1: Data Cleaning

Check your dataset for any outliers. 


```{r}
#Create a box plot to visualize outliers
algae_box_plot <- ggplot(algae_data, aes(x = Location, y = Density, fill = Location)) +
  geom_boxplot() +
  labs(
    title = "Algal Densities",
    x = "Location",
    y = "Algal Density"
  ) +
  scale_fill_manual(values = c("Location A" = "blue", "Location B" = "red"))

#View the box plot
algae_box_plot

```


### Q2: Visualization and Kernel Density Estimation (KDE)

Plot a Kernel Density Estimation (geom_density plot) to visualize the distribution of algal densities at both locations. 




```{r}
#Load ggplot2
library(ggplot2)

#Create a KDE plot
algae_KDE_plot <- ggplot(algae_data, aes(x = Density, fill = Location)) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Algal Densities",
    x = "Algal Density",
    y = "Density"
  ) +
  scale_fill_manual(values = c("Location A" = "blue", "Location B" = "red"))

#View the KDE plot
algae_KDE_plot
```

### Q3: Binomial Distribution
Suppose in a new survey, at each location, you take 10 random samples and in each sample, you identify whether a particular species of marine algae is present or not. Assume the probability of finding this species in a sample is 0.7 at Location A and 0.5 at Location B.

Simulate this scenario using a binomial distribution, and compare the probability of finding the species in at least 7 out of 10 samples at both locations.

```{r}
# Probability of finding the species in a sample
p_location_A <- 0.7
p_location_B <- 0.5

# Number of samples
n_samples <- 10

# Number of samples with the species found
k_success <- 7

# Calculate the probability of finding the species in at least 7 out of 10 samples
prob_location_A <- sum(dbinom(k_success:n_samples, n_samples, p_location_A))
prob_location_B <- sum(dbinom(k_success:n_samples, n_samples, p_location_B))

# Print the probabilities
cat("Probability of finding the species in at least 7 out of 10 samples at Location A:", prob_location_A, "\n")
cat("Probability of finding the species in at least 7 out of 10 samples at Location B:", prob_location_B, "\n")
```

### Q4: Poisson Distribution
Imagine a scenario where you are studying the occurrences of a particular rare marine event, such as the sighting of a rare marine species, over a set period at a specified location. Assume the average rate of occurrence is 3 per month.

Utilize a Poisson distribution to calculate the probability of observing exactly 5 occurrences in a month, and the probability of observing 3 or fewer occurrences in a month.

```{r}
# Average rate of occurrence
lambda <- 3

# Probability of observing exactly 5 occurrences in a month
five_occurrences <- dpois(5, lambda)
five_occurrences

# Probability of observing 3 or fewer occurrences in a month
less_three_occurrences <- ppois(3, lambda)
less_three_occurrences

# Print the probabilities
cat("Probability of observing exactly 5 occurrences in a month:", five_occurrences, "\n")
cat("Probability of observing 3 or fewer occurrences in a month:", less_three_occurrences, "\n")
```

### Q5: 
consider the following two lists. 

```{r}
list1 <- c(44.40, 47.70, 65.59, 50.71, 51.29, 67.15, 54.61, 37.35, 43.13, 45.54, 62.24, 53.60, 54.01, 51.11, 
           44.44, 67.87, 54.98, 30.33, 57.01, 45.27, 39.32, 47.82, 39.74, 42.71, 43.75, 33.13, 58.38, 51.53, 
           38.62, 62.54, 54.26, 47.05, 58.95, 58.78, 58.22, 56.89, 55.54, 49.38, 46.94, 46.20, 43.05, 47.92, 
           37.35, 71.69, 62.08, 38.77, 45.97, 45.33, 57.80, 49.17, 52.53, 49.71, 49.57, 63.69, 47.74, 65.16, 
           34.51, 55.85, 51.24, 52.16, 53.80, 44.98, 46.67, 39.81, 39.28, 53.04, 54.48, 50.53, 59.22, 70.50, 
           45.09, 26.91, 60.06, 42.91, 43.12, 60.26, 47.15, 37.79, 51.81, 48.61, 50.06, 53.85, 46.29, 56.44, 
           47.80, 53.32, 60.97, 54.35, 46.74, 61.49, 59.94, 55.48, 52.39, 43.72, 63.61, 44.00, 71.87, 65.33, 
           47.64, 39.74)

list2 <- c(44.34, 48.85, 41.30, 39.79, 30.73, 44.32, 33.23, 19.98, 39.30, 58.78, 36.37, 54.12, 20.73, 44.17, 
           52.79, 49.52, 46.59, 35.39, 32.25, 29.64, 46.76, 30.79, 37.64, 41.16, 72.66, 35.22, 48.53, 46.17, 
           30.57, 43.93, 66.67, 51.77, 45.62, 38.66, 14.20, 61.97, 23.09, 56.10, 73.64, 23.34, 55.53, 41.07, 
           21.42, 22.28, 20.98, 37.04, 23.07, 55.32, 76.50, 25.69, 56.82, 56.54, 49.98, 29.87, 43.21, 40.79, 
           53.44, 39.41, 59.65, 39.38, 60.79, 29.26, 26.10, 93.62, 38.75, 49.47, 54.55, 37.74, 52.75, 50.53, 
           41.77, 45.98, 44.49, 76.93, 33.88, 28.56, 45.57, 49.66, 51.55, 38.12, 29.05, 63.95, 39.76, 32.02, 
           41.46, 42.04, 61.65, 46.27, 56.31, 37.51, 48.22, 40.13, 46.42, 31.57, 25.34, 74.96, 54.01, 26.23, 
           35.83, 27.22)

```

These list were generated using the following code

set.seed(123)  # Setting a seed for reproducibility
list1 <- round(rnorm(100, mean = 50, sd = 10), 2)  # Generating 100 values from a normal distribution
list2 <- round(rnorm(100, mean = 45, sd = 15), 2)  # Generating 100 values from another normal distribution


Compare the distributions of these two lists to determine if they originate from the same distribution or from different distributions.

1. Use geom_density to create a density plot for each list on the same graph. Use different colors to distinguish between the two lists:
```{r}
# Load the ggplot2 library
library(ggplot2)

# Set the seed for reproducibility
set.seed(123)

# Create a data frame with the two lists
list1 <- round(rnorm(100, mean = 50, sd = 10), 2)
list2 <- round(rnorm(100, mean = 45, sd = 15), 2)
data <- data.frame(
  List = factor(rep(c("List 1", "List 2"), each = 100)),
  Value = c(list1, list2)
)
data

# Create a density plot
density_plot <- ggplot(data, aes(x = Value, fill = List)) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Density Plot",
    x = "Value",
    y = "Density"
  ) +
  scale_fill_manual(values = c("List 1" = "blue", "List 2" = "red"))

#View the Density Plot
density_plot

```

Examine the plot you have generated. Do you think list1 and list2 come from the same distribution or different distributions? Why?
Write down your observations and reasoning.


It seems they come from different distributions. The means are different and list 1 has a higher mean and less broad of a distribution. 

